Methods and Results

### 2021-03-30 ms.Rmd
Adding some fany tabling, but needs fixing

```
```{r loaddata, echo = FALSE, results = "hide"}
  # Tree
      data <- read.csv("./data/meta_data.csv")
      data <- data %>% 
              mutate(species2 = species)
      data$n_eff <- with(data, (N_C*N_T) / (N_C+N_T))

@@

>>>>

```
```{r loaddata, echo = FALSE, results = "hide"}
  # Tree
      data <- read.csv("./data/meta_data.csv")
      data <- data %>% 
              mutate(species2 = species)
      data$n_eff <- with(data, (4*(N_C*N_T)) / (N_C+N_T))

@@

```{r pretty_table}
table.model.r.gt <- table.model.r %>% 
                             gt() %>% 
          cols_label(n=md("**n**"),
             k=md("**k**"),
             mean=md("**Meta-analytic mean**"),
             CI=md("**95% CI**"),
             PI=md("**95% PI**"),
             I2_obsID=md("***I*<sup>2</sup><sub>residual</sub>\n(%)**"),
             I2_paperID=md("***I*<sup>2</sup><sub>study</sub>\n(%)**"),
             I2_nonphylo=md("***I*<sup>2</sup><sub>non-phylogeny</sub>\n(%)**"),
             I2_phylo=md("***I*<sup>2</sup><sub>phylogeny</sub>\n(%)**"),
             I2_total=md("***I*<sup>2</sup><sub>total</sub>    \n(%)**"),
             )                     %>%
      cols_align(align = "center") %>%
  tab_source_note(source_note = md("n = number of studies; k = number of effects; CI = confidence interval; PI = prediction interval; *I*<sup>2</sup> = heterogeneity")) #%>%
# tab_options(table.width=770)
```
